handle the labelled data in mrpkit

### 2023-07-01 README.Rmd
a few more edits to readme

For students and researchers who are comfortable with at least `glm()` and want
to conduct multilevel regression with post-stratification (MRP), `mrpkit`
provides a reproducible, opinionated, and highly structured workflow. Unlike
writing all the code yourself, using `mrpkit` proactively addresses many common
issues, and makes it possible for folks who are new to MRP to quickly conduct
their first analysis.

The package assists in setting up the survey data and relationships between
different variables in the sample and the population. From there, a substantial
amount of data cleaning is automated, saving time and reducing the risk of
coding errors. The package has native support for multilevel binomial and
Bernoulli models fit with lme4 and Stan (via brms and rstanarm) and also allows
for the use of custom modeling functions. Summaries and simple visualizations of
the resulting post-stratified estimates are provided.

>>>>

For students and researchers who are comfortable with at least `glm()` and want
to conduct multilevel regression with post-stratification (MRP), the `mrpkit` R
package provides a reproducible, opinionated, and highly structured workflow.
Unlike writing all the code yourself, using `mrpkit` proactively addresses many
common issues, and makes it possible for people who are new to MRP to quickly
conduct their first analysis.

The package first assists in setting up the survey data and relationships
between different variables in the sample and the population. From there, a
substantial amount of data cleaning is automated, saving time and reducing the
risk of coding errors. `mrpkit` has native support for multilevel binomial and
Bernoulli models fit with lme4 and Stan (via brms and rstanarm) and also allows
for the use of custom modeling functions. After model fitting, `mrpkit` handles
the post-stratification step, producing population and sub-population estimates.
Summary statistics and simple visualizations of the resulting MRP estimates are
provided.
